Objective-First Nanophotonic Design Plan

### 2012-09-21 plan/plan.tex
Added caption to figure.

To put things mathematically, we want to create software 
    to solve the following problem,
    \EE {the plan (single mode)}
        {\minimize&  f(x) + g(z) \\
        \subto&     A(z)x - b(z) = 0}
    where 
    \BI $x$ and $z$ are the variables representing 
            the field device our device produces and
            the structure of the device respectively,
    \I  $f(x)$ and $g(z)$ are our \emph{design objectives},
            which tell us the desirable properties 
            that we would like our device to achieve, and
    \I  $A(z)x - b(z)$ is the \emph{physics residual},
            the underlying physical laws which must be met. \EI

@@

\section{Capabilities of our software}\label{capabilities of our software}
We have implemented various 
    \emph{optimization paradigms} and \emph{structure parameterizations}
    which a user can arbitrarily combine in order to 
    design nanophotonic devices.

@@

And the user can also choose between the various structure parameterizations 
    which include density, boundary, 
    continuous, and combinatoric parameterizations.
These parameterizations describe the structure as either
    \BI a material density at every point in space;
    \I  a boundary between objects of different materials;
    \I  a set of continuously variable user-defined parameters; or 
    \I  a combination of user-defined objects. \EI

@@

\subsection{Definition of the field design objective}
Although $f_i(x_i)$ can take on virtually any form,
    we choose to define it very specifically as
    \E  {field design objective definition}
        {f_i(x_i) = \sum_j I_+(|c_{ij}\T x_i| - \alpha_{ij})
            + I_+(\beta_{ij} - |c_{ij}\T x_i|),}
    where $c_{ij} \in \comps^m$ and 
    $I_+$ is the indicator function on nonnegative reals,
    \E{}{I_+(u) = \begin{cases} 0 & u \ge 0, \\ 
                                \infty & u < 0. \end{cases}}

@@

\begin{pspicture}(6,5)(-6,-2)
\psset{gridcolor=green, subgridcolor=yellow}
    \let\psgrid\relax

@@

    % Parameterization
    \psframe(-.8,0.8)(.8,-0.4) 
    \rput(0,-0.7){\parbox{5cm}{\center structure\\ parameterization}}

    % Arrows
    \rput[r](-1.9,0.8){into sp}
    \psline(-1.6,1.8)(-1.6,0.2)
    \psline{->}(-1.6,0.2)(-1,0.2)

    \rput[l](1.9,0.8){out of sp}
    \psline(1.6,0.2)(1,0.2)
    \psline{<-}(1.6,1.8)(1.6,0.2)

    \rput[r](-4.3,3){initial input}
    \psline{->}(-4,3)(-2.4,3)

    \rput[l](4.3,3){output}
    \psline{<-}(4,3)(2.4,3)
\end{pspicture}

>>>>

To put things mathematically, we want to create software 
    to solve the following problem,
    \EE {the plan (single mode)}
        {\minimize&  f(x) + g(z) \\
        \subto&     A(z)x - b(z) = 0}
    where 
    \BI $x$ and $z$ are the variables representing 
            the \emph{field} our device produces and
            the \emph{structure} of the device respectively,
    \I  $f(x)$ and $g(z)$ are our \emph{design objectives},
            which tell us the desirable properties 
            that we would like our device to achieve, and
    \I  $A(z)x - b(z)$ is the \emph{physics residual},
            the underlying physical laws which must be met. \EI

@@

\section{Capabilities of our software}\label{capabilities of our software}
We have implemented various 
    \emph{optimization paradigms} and \emph{structure parameterizations}
    which a user can arbitrarily combine in order to 
    to solve \eq{the plan (multi-mode)}.

@@

Also, the user can choose between the various structure parameterizations 
    which include density, boundary, 
    continuous, and combinatoric parameterizations.
These parameterizations describe the structure as either
    \BI a material density at every point in space;
    \I  a boundary between objects of different materials;
    \I  a set of continuously variable user-defined parameters; or 
    \I  a selective combination of user-defined objects. \EI

@@

\subsection{Definition of the field design objective}
Although the field design objective $f_i(x_i)$ 
    can take on virtually any form,
    we choose to define it very specifically as
    \E  {field design objective definition}
        {f_i(x_i) = \sum_j I_+(|c_{ij}\T x_i| - \alpha_{ij})
            + I_+(\beta_{ij} - |c_{ij}\T x_i|),}
    where $c_{ij} \in \comps^m$ and 
    $I_+$ is the indicator function on nonnegative reals,
    \E{}{I_+(u) = \begin{cases} 0 & u \ge 0, \\ 
                                \infty & u < 0. \end{cases}}

@@

\begin{figure}[ht]\begin{center}
\begin{pspicture}(6,5)(-6,-2)
\psset{gridcolor=green, subgridcolor=yellow}
    \let\psgrid\relax

@@

    % Parameterization
    \psframe(-.8,0.8)(.8,-0.4) 
    \rput[t](0,-0.6){\parbox{3cm}{\center structure\\ parameterization}}

    % Arrows
    \rput[r](-4.3,3){$z_\text{guess}$}
    \psline{->}(-4,3)(-2.4,3)

    \rput[r](-1.9,0.8){$Q(z)$}
    \psline(-1.6,1.8)(-1.6,0.2)
    \psline{->}(-1.6,0.2)(-1,0.2)

    \rput[l](1.9,0.8){$\text{argmin}\, Q(z) + g(z)$}
    \psline(1.6,0.2)(1,0.2)
    \psline{<-}(1.6,1.8)(1.6,0.2)

    \rput[l](4.3,3){$z_\text{final}$}
    \psline{<-}(4,3)(2.4,3)
\end{pspicture}
\caption{Basic layout of our software.
        At the most basic level, the chosen optimization paradigm 
            accepts an initial structure $z_\text{guess}$
            and returns a final, optimized structure $z_\text{final}$.
        This is accomplished by repeatedly passing quadratic functions $Q(z)$ 
            to the structure parameterization,
            which returns an updated structure $z$
            which minimizes $Q(z) + g(z)$.}
\label{fig:strategy}
\end{center} \end{figure}
